### Whole Dataset

#### No transformation, inverse-variance method

```{r tbl-bias-all}
#| tbl-cap: Bias and heterogeneity in all primary studies

tar_read(bias_all) %>%
  subset(select = -c(tau, Rb)) %>%
  kable(booktabs = TRUE, longtable = TRUE, escape = FALSE, col.names = c(
    "N", "$\\beta$", "SE", "$p$", "$I^2$ (\\%)", "$H^2$", "$\\tau^2$"
  )) %>%
  add_header_above(c(" " = 1, "Egger's test" = 3, "Heterogeneity [95% CI]" = 3)) %>%
  kable_styling(font_size = 7, latex_options = c("repeat_header"))

```

```{r tbl-meta-all}
#| tbl-cap: Pooling effect size in all primary studies

sub_meta <- tar_read(meta_all) %>%
  subset(!.$Exclude, select = -c(Exclude))

to_bold  <- sub_meta %>% {which(.$Author %in% c("Random", "Fixed"))}
to_color <- sub_meta %>% {which(.$Author == "Prediction")}

sub_meta %>%
  kable(booktabs = TRUE, longtable = TRUE) %>%
  add_header_above(c(" " = 2, "Prevalence" = 4, "Weight (%)" = 2)) %>%
  row_spec(to_bold, bold = TRUE) %>%
  row_spec(to_color, bold = TRUE, background = "#D8DEE9") %>%
  kable_styling(font_size = 7, latex_options = c("repeat_header"))

```

#### Logit link function, GLMM method

```{r tbl-bias-glmm}
#| tbl-cap: Bias and heterogeneity in all primary studies

tar_read(bias_glmm) %>%
  subset(select = -c(tau, Rb)) %>%
  kable(booktabs = TRUE, longtable = TRUE, escape = FALSE, col.names = c(
    "N", "$\\beta$", "SE", "$p$", "$I^2$ (\\%)", "$H^2$", "$\\tau^2$"
  )) %>%
  add_header_above(c(" " = 1, "Egger's test" = 3, "Heterogeneity [95% CI]" = 3)) %>%
  kable_styling(font_size = 7, latex_options = c("repeat_header"))

```

```{r tbl-meta-glmm}
#| tbl-cap: Pooling effect size in all primary studies

sub_meta <- tar_read(meta_glmm) %>%
  subset(!.$Exclude, select = -c(Exclude))

to_bold  <- sub_meta %>% {which(.$Author %in% c("Random", "Fixed"))}
to_color <- sub_meta %>% {which(.$Author == "Prediction")}

sub_meta %>%
  kable(booktabs = TRUE, longtable = TRUE) %>%
  add_header_above(c(" " = 2, "Prevalence" = 4, "Weight (%)" = 2)) %>%
  row_spec(to_bold, bold = TRUE) %>%
  row_spec(to_color, bold = TRUE, background = "#D8DEE9") %>%
  kable_styling(font_size = 7, latex_options = c("repeat_header"))

```


#### No transformation, inverse-variance method, preserved outliers

```{r tbl-bias-all-nodrop}
#| tbl-cap: Bias and heterogeneity in all primary studies

tar_read(bias_all_nodrop) %>%
  subset(select = -c(tau, Rb)) %>%
  kable(booktabs = TRUE, longtable = TRUE, escape = FALSE, col.names = c(
    "N", "$\\beta$", "SE", "$p$", "$I^2$ (\\%)", "$H^2$", "$\\tau^2$"
  )) %>%
  add_header_above(c(" " = 1, "Egger's test" = 3, "Heterogeneity [95% CI]" = 3)) %>%
  kable_styling(font_size = 7, latex_options = c("repeat_header"))

```

```{r tbl-meta-all-nodrop}
#| tbl-cap: Pooling effect size in all primary studies

sub_meta <- tar_read(meta_all_nodrop) %>%
  subset(!.$Exclude, select = -c(Exclude))

to_bold  <- sub_meta %>% {which(.$Author %in% c("Random", "Fixed"))}
to_color <- sub_meta %>% {which(.$Author == "Prediction")}

sub_meta %>%
  kable(booktabs = TRUE, longtable = TRUE) %>%
  add_header_above(c(" " = 2, "Prevalence" = 4, "Weight (%)" = 2)) %>%
  row_spec(to_bold, bold = TRUE) %>%
  row_spec(to_color, bold = TRUE, background = "#D8DEE9") %>%
  kable_styling(font_size = 7, latex_options = c("repeat_header"))

```

#### Logit link function, GLMM method, preserved outliers

```{r tbl-bias-glmm-nodrop}
#| tbl-cap: Bias and heterogeneity in all primary studies

tar_read(bias_nodrop_glmm) %>%
  subset(select = -c(tau, Rb)) %>%
  kable(booktabs = TRUE, longtable = TRUE, escape = FALSE, col.names = c(
    "N", "$\\beta$", "SE", "$p$", "$I^2$ (\\%)", "$H^2$", "$\\tau^2$"
  )) %>%
  add_header_above(c(" " = 1, "Egger's test" = 3, "Heterogeneity [95% CI]" = 3)) %>%
  kable_styling(font_size = 7, latex_options = c("repeat_header"))

```

```{r tbl-meta-glmm-nodrop}
#| tbl-cap: Pooling effect size in all primary studies

sub_meta <- tar_read(meta_nodrop_glmm) %>%
  subset(!.$Exclude, select = -c(Exclude))

to_bold  <- sub_meta %>% {which(.$Author %in% c("Random", "Fixed"))}
to_color <- sub_meta %>% {which(.$Author == "Prediction")}

sub_meta %>%
  kable(booktabs = TRUE, longtable = TRUE) %>%
  add_header_above(c(" " = 2, "Prevalence" = 4, "Weight (%)" = 2)) %>%
  row_spec(to_bold, bold = TRUE) %>%
  row_spec(to_color, bold = TRUE, background = "#D8DEE9") %>%
  kable_styling(font_size = 7, latex_options = c("repeat_header"))

```


### Grouped by year

#### No transformation, inverse-variance method

```{r tbl-bias-year}
#| tbl-cap: Bias and heterogeneity in all primary studies, subsetted by year

tar_load(bias_eda)
bias_eda$year %>% report_bias()

```

```{r tbl-meta-year}
#| tbl-cap: Pooling effect size in all primary studies, subsetted by year

tar_load(meta_eda)
meta_eda$year %>% report_meta()

```

#### No transformation, inverse-variance method, preserved outliers

```{r tbl-bias-year-nodrop}
#| tbl-cap: Bias and heterogeneity in all primary studies, subsetted by year

tar_load(bias_eda_nodrop)
bias_eda_nodrop$year %>% report_bias()

```

```{r tbl-meta-year-nodrop}
#| tbl-cap: Pooling effect size in all primary studies, subsetted by year

tar_load(meta_eda_nodrop)
meta_eda_nodrop$year %>% report_meta()

```

### Grouped by continent

#### No transformation, inverse-variance method

```{r tbl-bias-continent}
#| tbl-cap: Bias and heterogeneity in all primary studies, subsetted by continents

bias_eda$continent %>% report_bias()

```

```{r tbl-meta-continent}
#| tbl-cap: Pooling effect size in all primary studies, subsetted by continents

meta_eda$continent %>% report_meta()

```

#### No transformation, inverse-variance method, preserved outliers

```{r tbl-bias-continent-nodrop}
#| tbl-cap: Bias and heterogeneity in all primary studies, subsetted by continents

bias_eda_nodrop$continent %>% report_bias()

```

```{r tbl-meta-continent-nodrop}
#| tbl-cap: Pooling effect size in all primary studies, subsetted by continents

meta_eda_nodrop$continent %>% report_meta()

```

### Grouped by region

#### No transformation, inverse-variance method

```{r tbl-bias-region}
#| tbl-cap: Bias and heterogeneity in all primary studies, subsetted by regions

bias_eda$region %>% report_bias()

```

```{r tbl-meta-region}
#| tbl-cap: Pooling effect size in all primary studies, subsetted by regions

meta_eda$region %>% report_meta()

```

#### No transformation, inverse-variance method, preserved outliers

```{r tbl-bias-region-nodrop}
#| tbl-cap: Bias and heterogeneity in all primary studies, subsetted by regions

bias_eda_nodrop$region %>% report_bias()

```

```{r tbl-meta-region-nodrop}
#| tbl-cap: Pooling effect size in all primary studies, subsetted by regions

meta_eda_nodrop$region %>% report_meta()

```

### Grouped by criteria

#### No transformation, inverse-variance method

```{r tbl-bias-clean-criteria}
#| tbl-cap: Bias and heterogeneity in all primary studies, subsetted by diagnostic criteria

bias_eda$clean_criteria %>% report_bias()

```

```{r tbl-meta-clean-criteria}
#| tbl-cap: Pooling effect size in all primary studies, subsetted by diagnostic criteria

meta_eda$clean_criteria %>% report_meta()

```

#### No transformation, inverse-variance method, preserved outliers

```{r tbl-bias-clean_criteria-nodrop}
#| tbl-cap: Bias and heterogeneity in all primary studies, subsetted by diagnostic criteria

bias_eda_nodrop$clean_criteria %>% report_bias()

```

```{r tbl-meta-clean_criteria-nodrop}
#| tbl-cap: Pooling effect size in all primary studies, subsetted by diagnostic criteria

meta_eda_nodrop$clean_criteria %>% report_meta()

```

### Grouped by instrument

#### No transformation, inverse-variance method

```{r tbl-bias-clean-instrument}
#| tbl-cap: Bias and heterogeneity in all primary studies, subsetted by psychometric instrument

bias_eda$clean_instrument %>% report_bias()

```

```{r tbl-meta-clean-instrument}
#| tbl-cap: Pooling effect size in all primary studies, subsetted by psychometric instrument

meta_eda$clean_instrument %>% report_meta()

```

#### No transformation, inverse-variance method, preserved outliers

```{r tbl-bias-clean_instrument-nodrop}
#| tbl-cap: Bias and heterogeneity in all primary studies, subsetted by psychometric instrument

bias_eda_nodrop$clean_instrument %>% report_bias()

```

```{r tbl-meta-clean_instrument-nodrop}
#| tbl-cap: Pooling effect size in all primary studies, subsetted by psychometric instrument

meta_eda_nodrop$clean_instrument %>% report_meta()

```

