---
author: Aly Lamuri
title: Meta-Analysis on Selected Articles
format:
  pdf:
    keep-tex: true
    number-sections: true
bibliography: ref.bib
knitr:
  opts_chunk:
    echo: false
    error: false
    warning: false
    message: false
    fig.width: 10
    fig.height: 8
    comment: "|"
header-includes:
- \usepackage{typearea}
---

```{r init}

pkgs <- c("magrittr", "targets", "kableExtra")
pkgs_load <- sapply(pkgs, library, character.only = TRUE)

options(digits = 2)
options(knitr.kable.NA = "")

report_bias <- function(bias) {
  res <- bias %>%
    subset(select = -c(tau, Rb)) %>%
    kable(booktabs = TRUE, longtable = TRUE, escape = FALSE, col.names = c(
      "Label", "K", "$\\beta$", "SE", "$p$", "$I^2$ (\\%)", "$H^2$", "$\\tau^2$"
    )) %>%
    add_header_above(c(" " = 2, "Egger's test" = 3, "Heterogeneity [95% CI]" = 3)) %>%
    kable_styling(font_size = 7, latex_options = c("repeat_header"))

  return(res)
}

report_meta <- function(meta) {
  sub_meta <- meta %>% subset(!.$Exclude, select = -c(Exclude))
  to_bold  <- sub_meta %>% {which(.$Author %in% c("Random", "Fixed"))}
  to_color <- sub_meta %>% {which(.$Author == "Prediction")}
  res <- sub_meta %>%
    kable(booktabs = TRUE, longtable = TRUE) %>%
    add_header_above(c(" " = 3, "Prevalence" = 4, "Weight (%)" = 2)) %>%
    row_spec(to_bold, bold = TRUE) %>%
    row_spec(to_color, bold = TRUE, background = "#D8DEE9") %>%
    kable_styling(font_size = 7, latex_options = c("repeat_header"))

  return(res)
}

getES <- function(meta, type = "Random") {
  sub_meta <- meta %>% subset(.$Author == type)
  return(sub_meta)
}

reportES <- function(ES) {
  msg <- sprintf("%s%% [%s%%; p %s]", round(ES$`%`, 2), ES$`95% CI`, ES$p)
  return(msg)
}

n_eda <- sapply(tar_read(bias_eda), \(x) sum(x$N))

es_all <- getES(tar_read(meta_all)) %>% reportES()

es_eda <- lapply(tar_read(meta_eda), getES) %>%
  lapply("[[", "%") %>%
  sapply(mean)

es_author <- getES(tar_read(meta_author)) %>%
  extract2("%") %>%
  mean(na.rm = TRUE)

tar_load(meta_reg)

```

# Executive Summary {-}

- Two datasets are used:
  - Raw data: Includes all extracted studies, still contains duplicates (N = `r nrow(tar_read(tbl))`)
  - Clean data: Removed duplicates of extracted studies (N = `r nrow(tar_read(tbl_clean))`)
- Effect size was pooled for the prevalence of diabetes
- Analysis approach:
  - Raw data: Reproduce the result reported in included reviews, also to measure bias and heterogeneity
  - Clean data: Conduct meta-analysis on a subset of clean data, grouped by year, countries, diagnostic criteria, and psychometric instruments
  - General steps:
    - Extracted studies which 95% CI expands beyond the pooled confidence interval is regarded as outliers
    - Outliers were removed when pooling the effect size in favor of improving the homogeneity:
      - Re-analysis of included reviews contains `r sum(tar_read(bias_author)$N)` studies without outliers
      - Exploratory data analysis (EDA) grouped by year contains `r n_eda["year"]` studies without outliers
      - EDA grouped by country contains `r n_eda["clean_country"]` studies without outliers
      - EDA grouped by diagnostic criteria contains `r n_eda["clean_criteria"]` studies without outliers
      - EDA grouped by psychometric instrument contains `r n_eda["clean_instrument"]` studies without outliers
      - Meta-analysis on whole clean data contains `r sum(tar_read(bias_all)$N)` studies without outliers
    - Random effect model is fitted for all meta-analysis procedure
    - Subgroup meta-analysis in case of effect size differences when conducting the EDA procedure
    - Meta-regression using subgroup variables as covariates
- **Insight:**
  - Using whole clean data, I found that the prevalence of depression is `r es_all`
  - Meanwhile, EDA procedure resulted in the following mean of prevalence:
    - Grouped by year: `r es_eda["year"]`%
    - Grouped by country: `r es_eda["clean_country"]`%
    - Grouped by diagnostic criteria: `r es_eda["clean_criteria"]`%
    - Grouped by psychometric instrument: `r es_eda["clean_instrument"]`%
  - Considering the number of outliers and differences between EDA result and whole dataset meta-analysis, it appears that subgroup analysis is necessary
  - Results from subgroup analysis in @sec-subgroup indicates higher within difference than between difference, implying high variance even within the subgroup
  - Meta-regression indicates a growing prevalence of depression at the rate of `r round(meta_reg$b[2] * 100, 2)`% per year
- What to include in the report?
  - @tbl-bias-author
  - @tbl-bias-all
  - @tbl-meta-all
  - @sec-subgroup-year
  - @sec-subgroup-criteria
  - @sec-metareg
  - @fig-metareg

{{< pagebreak >}}

# Re-analysis of Included Reviews

```{r tbl-bias-author}
#| tbl-cap: Bias and heterogeneity in included reviews

tar_read(bias_author) %>% report_bias()

```

```{r tbl-meta-author}
#| tbl-cap: Re-analysis of included reviews

tar_read(meta_author) %>% report_meta()

```

{{< pagebreak >}}

# Exploratory Data Analysis

## Whole Dataset

### No transformation, inverse-variance method

```{r tbl-bias-all}
#| tbl-cap: Bias and heterogeneity in all primary studies

tar_read(bias_all) %>%
  subset(select = -c(tau, Rb)) %>%
  kable(booktabs = TRUE, longtable = TRUE, escape = FALSE, col.names = c(
    "N", "$\\beta$", "SE", "$p$", "$I^2$ (\\%)", "$H^2$", "$\\tau^2$"
  )) %>%
  add_header_above(c(" " = 1, "Egger's test" = 3, "Heterogeneity [95% CI]" = 3)) %>%
  kable_styling(font_size = 7, latex_options = c("repeat_header"))

```

```{r tbl-meta-all}
#| tbl-cap: Pooling effect size in all primary studies

sub_meta <- tar_read(meta_all) %>%
  subset(!.$Exclude, select = -c(Exclude))

to_bold  <- sub_meta %>% {which(.$Author %in% c("Random", "Fixed"))}
to_color <- sub_meta %>% {which(.$Author == "Prediction")}

sub_meta %>%
  kable(booktabs = TRUE, longtable = TRUE) %>%
  add_header_above(c(" " = 2, "Prevalence" = 4, "Weight (%)" = 2)) %>%
  row_spec(to_bold, bold = TRUE) %>%
  row_spec(to_color, bold = TRUE, background = "#D8DEE9") %>%
  kable_styling(font_size = 7, latex_options = c("repeat_header"))

```

### Logit link function, GLMM method

```{r tbl-bias-glmm}
#| tbl-cap: Bias and heterogeneity in all primary studies

tar_read(bias_glmm) %>%
  subset(select = -c(tau, Rb)) %>%
  kable(booktabs = TRUE, longtable = TRUE, escape = FALSE, col.names = c(
    "N", "$\\beta$", "SE", "$p$", "$I^2$ (\\%)", "$H^2$", "$\\tau^2$"
  )) %>%
  add_header_above(c(" " = 1, "Egger's test" = 3, "Heterogeneity [95% CI]" = 3)) %>%
  kable_styling(font_size = 7, latex_options = c("repeat_header"))

```

```{r tbl-meta-glmm}
#| tbl-cap: Pooling effect size in all primary studies

sub_meta <- tar_read(meta_glmm) %>%
  subset(!.$Exclude, select = -c(Exclude))

to_bold  <- sub_meta %>% {which(.$Author %in% c("Random", "Fixed"))}
to_color <- sub_meta %>% {which(.$Author == "Prediction")}

sub_meta %>%
  kable(booktabs = TRUE, longtable = TRUE) %>%
  add_header_above(c(" " = 2, "Prevalence" = 4, "Weight (%)" = 2)) %>%
  row_spec(to_bold, bold = TRUE) %>%
  row_spec(to_color, bold = TRUE, background = "#D8DEE9") %>%
  kable_styling(font_size = 7, latex_options = c("repeat_header"))

```


## Grouped by year

```{r tbl-bias-year}
#| tbl-cap: Bias and heterogeneity in all primary studies, subsetted by year

tar_load(bias_eda)
bias_eda$year %>% report_bias()

```

```{r tbl-meta-year}
#| tbl-cap: Pooling effect size in all primary studies, subsetted by year

tar_load(meta_eda)
meta_eda$year %>% report_meta()

```

## Grouped by country

```{r tbl-bias-country}
#| tbl-cap: Bias and heterogeneity in all primary studies, subsetted by countries

tar_load(bias_eda)
bias_eda$clean_country %>% report_bias()

```

```{r tbl-meta-country}
#| tbl-cap: Pooling effect size in all primary studies, subsetted by countries

tar_load(meta_eda)
meta_eda$clean_country %>% report_meta()

```

## Grouped by criteria

```{r tbl-bias-criteria}
#| tbl-cap: Bias and heterogeneity in all primary studies, subsetted by diagnostic criteria

tar_load(bias_eda)
bias_eda$clean_criteria %>% report_bias()

```

```{r tbl-meta-criteria}
#| tbl-cap: Pooling effect size in all primary studies, subsetted by diagnostic criteria

tar_load(meta_eda)
meta_eda$clean_criteria %>% report_meta()

```

{{< pagebreak >}}

\KOMAoptions{paper=landscape,pagesize}
\recalctypearea

## Grouped by instrument

```{r tbl-bias-instrument}
#| tbl-cap: Bias and heterogeneity in all primary studies, subsetted by psychometric instruments

tar_load(bias_eda)
bias_eda$clean_instrument %>% report_bias()

```

```{r tbl-meta-instrument}
#| tbl-cap: Pooling effect size in all primary studies, subsetted by psychometric instruments

tar_load(meta_eda)
meta_eda$clean_instrument %>% report_meta()

```

{{< pagebreak >}}

\KOMAoptions{paper=portrait,pagesize}
\recalctypearea

# Sub-group Meta Analysis, Inverse-Variance Method {#sec-subgroup}

## Grouped by year of review {#sec-subgroup-year}

```{r lst-subgroup-year}

report_subgroup <- function(mod, meta) {
  note <- sprintf(
    "Random model: Q = %s, df = %s, p = %s. Common model: Q = %s, df = %s, p = %s",
    round(mod$Q.b.random, 2),
    round(mod$df.Q.b.random, 2),
    round(mod$pval.Q.b.random, 3),
    round(mod$Q.b.common, 2),
    round(mod$df.Q.b.common, 2),
    round(mod$pval.Q.b.common, 3)
  )

  res <- meta %>%
    kable(booktabs = TRUE, longtable = TRUE, escape = FALSE, col.names = c(
      "Label", "K", "Fixed (\\%)", "Random (\\%)", "$I^2$ (\\%)", "$H^2$", "$\\tau^2$"
    )) %>%
    add_header_above(c(" " = 2, "Prevalence [95% CI]" = 2, "Heterogeneity" = 3)) %>%
    footnote(general = note, general_title = "Between group differences") %>%
    kable_styling(font_size = 10, latex_options = c("repeat_header"))
  return(res)
}

report_subgroup(
  tar_read(subgroup_analysis)$year,
  tar_read(meta_subgroup)$year
)

```

## Grouped by published year {#sec-subgroup-criteria}

```{r lst-subgroup-incl-year}

report_subgroup(
  tar_read(subgroup_analysis)$incl_year,
  tar_read(meta_subgroup)$incl_year
)

```

## Grouped by criteria {#sec-subgroup-criteria}

```{r lst-subgroup-criteria}

report_subgroup(
  tar_read(subgroup_analysis)$clean_criteria,
  tar_read(meta_subgroup)$clean_criteria
)

```

::: {.content-hidden}

## Grouped by country {#sec-subgroup-country}

```{r lst-subgroup-country, eval = FALSE}

report_subgroup(
  tar_read(subgroup_analysis)$clean_country,
  tar_read(meta_subgroup)$clean_country %>% {.[order(.$N, decreasing = TRUE), ]}
)

```

{{< pagebreak >}}

\KOMAoptions{paper=landscape,pagesize}
\recalctypearea

## Grouped by instrument {#sec-subgroup-instrument}

```{r lst-subgroup-instrument, eval = FALSE}

report_subgroup(
  tar_read(subgroup_analysis)$clean_instrument,
  tar_read(meta_subgroup)$clean_instrument %>% {.[order(.$N, decreasing = TRUE), ]}
)

```

{{< pagebreak >}}

\KOMAoptions{paper=portrait,pagesize}
\recalctypearea

:::

# Meta-regression, Inverse-Variance Method {#sec-metareg}

```{r}
#| fig-cap: Diagnostic plot of the meta-regression model
#| fig-pos: H

 #tar_read(meta_reg) %T>% plot()
tar_read(meta_reg) %>% summary()

```

{{< pagebreak >}}

\KOMAoptions{paper=landscape,pagesize}
\recalctypearea

```{r fig-metareg}
#| fig-cap: Bubble plot on a meta-regression model incorporating year and diagnostic criteria as covariates in determining the prevalence of depression
#| fig-pos: H

tar_read(plt_metareg)

```

{{< pagebreak >}}

\KOMAoptions{paper=portrait,pagesize}
\recalctypearea

# Sub-group Meta Analysis, GLMM Method {#sec-subgroup-glmm}

## Grouped by year of review {#sec-subgroup-year}

```{r lst-subgroup-glmm-year}

report_subgroup(
  tar_read(subgroup_glmm)$year,
  tar_read(meta_subgroup_glmm)$year
)

```

## Grouped by published year {#sec-subgroup-glmmcriteria}

```{r lst-subgroup-glmmincl-year}

report_subgroup(
  tar_read(subgroup_glmm)$incl_year,
  tar_read(meta_subgroup_glmm)$incl_year
)

```

## Grouped by criteria {#sec-subgroup-glmmcriteria}

```{r lst-subgroup-glmmcriteria}

report_subgroup(
  tar_read(subgroup_glmm)$clean_criteria,
  tar_read(meta_subgroup_glmm)$clean_criteria
)

```

# Meta-regression, GLMM Method {#sec-subgroup-glmm}

```{r}
#| fig-cap: Diagnostic plot of the meta-regression model
#| fig-pos: H

 #tar_read(meta_reg) %T>% plot()
tar_read(meta_reg_glmm) %>% summary()

```

{{< pagebreak >}}

\KOMAoptions{paper=landscape,pagesize}
\recalctypearea

```{r fig-metareg-glmm}
#| fig-cap: Bubble plot on a meta-regression model incorporating year and diagnostic criteria as covariates in determining the prevalence of depression
#| fig-pos: H

tar_read(plt_metareg_glmm)

```

{{< pagebreak >}}

\KOMAoptions{paper=portrait,pagesize}
\recalctypearea

